---
title: "Lab 07 - Modelling course evaluations"
author: "Helen Miller"
date: "`r Sys.Date()`"
output: html_document
---

### Packages and Data

```{r load-packages, message=FALSE, echo=TRUE}
library(tidyverse)
library(tidymodels)

```


```{r read-data}
evals<-read.csv("data/evals.csv", row.names=1)
```


# Exercise 1: Exploratory Data Analysis

1.  Visualize the distribution of `score` in the dataframe `evals`.

```{r viz-score}
vis_score <- evals %>% 
  ggplot(mapping=aes(x=score)) +
  geom_histogram(bins=20)
vis_score
```
```{r}
summary_stats <- evals %>% 
  summarise(mean = mean(score), median = median(score))
summary_stats
```

*The distribution is left skewed, and centred  between 4.1 and 4.3*

2.  Visualize and describe the relationship between `score` and `bty_avg` using `geom_point()` to represent the data. 

```{r scatterplot}
bty_v_score <- evals %>% 
  ggplot(mapping=aes(x=bty_avg, y=score)) +
  geom_jitter()
bty_v_score
```

*Jitter adds a small amount of random noise to the plot, which allows you to better see the density of points on the plot.*

# Exercise 2: Simple Linear regression with a numerical predictor

1. Fit a linear model called `score_bty_fit` to predict average professor evaluation `score` from average beauty rating (`bty_avg`). Print the regression output using `tidy()`.

```{r fit-score_bty_fit}
# remove eval = FALSE from the code chunk options after filling in the blanks
model <- linear_reg() %>%
  set_engine("lm") %>%
  fit(score ~ bty_avg, data = evals)
```

```{r tidy-score_bty_fit}
# remove eval = FALSE from the code chunk options after filling in the blanks
tidy(model)
```

*score-hat = 3.880 + 0.067(bty_avg)*

2. Plot the data again using `geom_jitter()`, and add the regression line.

```{r viz-score_bty_fit,eval=FALSE}
new_bty_v_score <- evals %>% 
  ggplot(mapping=aes(x=bty_avg, y=score)) +
  geom_jitter() +
  geom_smooth(method=lm)
new_bty_v_score
```

3. Interpret the slope of the linear model in context of the data.

*For an increase of 1 in average beauty score, we expect the overall score to increase by 0.067 on average*

4. Interpret the intercept of the linear model in context of the data. Comment on whether or not the intercept makes sense in this context.

*At a beauty score of 0, we expect the overall score of the professor to be 3.88 on average. This does make a fair bit of sense in context.*

5. Determine the $R^2$ of the model and interpret it in the context of the data.

```{r R2}
# remove eval = FALSE from the code chunk options after filling in the blanks
glance(model)$r.squared
```

*3.5% of the variation in overall score can be explained by its linear relationship with average beauty score.*

6. Make a plot of residuals vs. predicted values for the model above.

```{r viz-score_bty_fit-diagnostic}
# remove eval = FALSE from the code chunk options after filling in the blanks
score_bty_aug <- augment(model$fit)

ggplot(score_bty_aug, mapping=aes(x=.fitted, y=.resid)) +
  geom_jitter() +
  geom_hline(linetype='dashed', yintercept=0)
```
*There is a faint pattern on the residual plot, so it does not look like a linear model is appropriate*

# Exercise 3: Simple Linear regression with a categorical predictor

0. Look at the variable rank, and determine the frequency of each category level.

```{r}
# ... 
```

1. Fit a new linear model called `score_rank_fit` to predict average professor evaluation `score` based on `rank` of the professor.

```{r fit-score_rank_fit}
# fit model

# tidy model output
```

*Add your narrative here.*

2. Fit a new linear model called `score_gender_fit` to predict average professor evaluation `score` based on `gender` of the professor. 

```{r fit-score_gender_fit}
# fit model

# tidy model output
```

```{r score_gender_intercept, eval=FALSE}
# remove eval = FALSE from the code chunk options
score_gender_intercept <- tidy(score_gender_fit) %>% 
  filter(term == "(Intercept)") %>%
  select(estimate) %>%
  pull()
```

```{r score_gender_slope, eval=FALSE}
# remove eval = FALSE from the code chunk options
score_gender_slope <- tidy(score_gender_fit) %>% 
  filter(term == "gendermale") %>%
  select(estimate) %>%
  pull()
```

*Add your narrative here. Use in-line code!*

# Exercise 4: Multiple linear regression

1. Fit a multiple linear regression model, predicting average professor evaluation `score` based on average beauty rating (`bty_avg`) and `gender.`

```{r fit-score_bty_gender_fit}
# fit model

# tidy model output
```

*Add your narrative here.*

```{r eval = FALSE}
ggplot(___) + ...
```

2. What percent of the variability in `score` is explained by the model `score_bty_gender_fit`. 

```{r}
# ...
```


3. What is the equation of the line corresponding to just male professors?

*Add your equation here.*

4. For two professors who received the same beauty rating, which gender tends to have the higher course evaluation score?

*Add your narrative here.*

5. How does the relationship between beauty and evaluation score vary between male and female professors?

*Add your narrative here.*

6. How do the adjusted $R^2$ values of `score_bty_fit` and `score_bty_gender_fit` compare? 

```{r eval=FALSE}
# remove eval = FALSE from the code chunk options after filling in the blanks
glance(___)$adj.r.squared
glance(___)$adj.r.squared
```

*Add your narrative here.*

7. Compare the slopes of `bty_avg` under the two models (`score_bty_fit` and `score_bty_gender_fit`).

*Add your narrative here.*

# Exercise 5: Interpretation of log-transformed response variables

If you do not know how to use LaTeX, do this exercise with pen and paper.
